---
mainfont: Nunito
font: Nunito
fontsize: 14 pt
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
    keep_tex: false
params: 
  file_path: data
  school_name: x
  set_title: x
  teacher_name: x
geometry: "left=1in,right=1in,top=1in,bottom=0.6in"

---

```{r rmarkdown-setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)

```


```{r setup, include=FALSE}

if(params$teacher_name %in% district_time2$TeacherLast){
  teacher_2 <- subset(district_time2, district_time2$TeacherLast == params$teacher_name)  
} else {
teacher_2 <- data.frame()
}

if(dim(teacher_2)[1] >= 5 & mean(teacher_2$OverallScore, na.rm = T) != "NaN"){
  class_for_plotting_2 <- prep_classroom_plots(teacher_2)
} else {
  class_for_plotting_2 <- data.frame()
}



```

##  Classroom-level report for `r  params$teacher_name`, Timepoint 2

This is a classroom-level report for student performance on SELweb EE in `r params$teacher_name`'s classroom. 

The summary plot shows what proportion of students fall into each of the 4 performance levels (above average, average, below average, and well-below average). The summary table shows standard scores for SELweb EE competencies for each student in this classroom. See the attached appendix for more information about SELweb EE competencies, standard scores, and performance levels. 


## Summary Plot for Classroom
```{r setup-pdf, echo = FALSE, warning = FALSE, results = "asis"}

n_class_2 <- dim(subset(district_time2, district_time2$School == params$school_name & district_time2$TeacherLast == params$teacher_name))[1]
  
if(dim(class_for_plotting_2)[1] > 0 ){
  
  make_summary_plot_pdf(class_for_plotting_2, params$teacher_name, n_class_2)
} else {
  print("Not enough data collected in Timepoint 2")
  cat("\n\n\n")
}
 
cat(" \n\n\n")

```
Above average: $\geq$ 115; At or around average: 90-114; Below average: 70-89; Well below average: $\leq$ 69


## Summary Table for Classroom
```{r summary-table, echo = FALSE}

if(length(teacher_2) > 0){
  
  student_data_for_table_2 <- teacher_2 %>% 
    arrange(LastName) %>% 
    select("Student ID" = StudentID, Grade, "First Name" = FirstName, "Last Name" = LastName, "Overall" = OverallScore,
           "Emotion Recognition" = ERScore, "Social Perspective-Taking" = SPTScore, "Social Problem-Solving" = SPSScore, "Self Control" = SCScore) %>% 
    replace(is.na(.), "")
  
  ### Summary Scores by School
  kable(student_data_for_table_2, "latex", booktabs = T, align = "lcccccccc", linesep = "") %>% 
    kable_styling(latex_options = c("striped", "bordered"), full_width = F) %>% 
    column_spec(2:9, width = "1.3cm") 

  
} else {
  print("Not enough data collected in Timepoint 2")
  cat("\n\n\n")
}
 


cat('\n\n\n\n')

```

\includepdf[pages={-}]{report_appendix.pdf}
