---
mainfont: Nunito
font: Nunito
fontsize: 14 pt
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
    keep_tex: false
params: 
  file_path: data
  school_name: x
  set_title: x
  teacher_name: "De La Rosa"
  version: x
geometry: "left=1in,right=1in,top=1in,bottom=0.6in"



---

```{r rmarkdown-setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)

```



```{r setup, include=FALSE}

# check to see if params$teacher_name actually tested in each time point
if(params$teacher_name %in% district$TeacherLast){
  teacher_1 <- subset(district, district$TeacherLast == params$teacher_name) 
} else {
teacher_1 <- data.frame()
}


if(version == "EE"){
  if(dim(teacher_1)[1] >= 5 & mean(teacher_1$OverallScore, na.rm = T) != "NaN") {
    class_for_plotting_1 <- prep_classroom_plots(teacher_1)
  } else {
    class_for_plotting_1 <- data.frame()
  }
} else if(version == "LE"){
    if(dim(teacher_1)[1] >= 5 & mean(teacher_1$SEL.SS, na.rm = T) != "NaN") {
    class_for_plotting_1 <- prep_classroom_plots_le(teacher_1)
  } else {
    class_for_plotting_1 <- data.frame()
  }
}

```

##  Classroom-level report for `r  params$teacher_name`, Timepoint 1

This is a classroom-level report for student performance on SELweb `r  params$version` in `r params$teacher_name`'s classroom. 

The summary plot shows what proportion of students fall into each of the 4 performance levels (above average, average, below average, and well-below average). The summary table shows standard scores for SELweb `r  params$version` competencies for each student in this classroom. See the attached appendix for more information about SELweb `r  params$version` competencies, standard scores, and performance levels. 


## Summary Plot for Classroom
```{r setup-pdf, echo = FALSE, warning = FALSE, results = "asis"}

n_class <- dim(subset(district, district$School == params$school_name & district$TeacherLast == params$teacher_name))[1]
  
if(dim(class_for_plotting_1)[1] > 0 ){
  if(version == "EE"){
    make_summary_plot_pdf(class_for_plotting_1, params$teacher_name, n_class)
  } else if(version == "LE"){
    make_summary_plot_pdf_le(class_for_plotting_1, params$teacher_name, n_class)
  }
  
} else {
  print("Not enough data collected in Timepoint 2")
  cat("\n\n\n")
}
 
cat(" \n\n\n")

```
Above average: $\geq$ 115; At or around average: 90-114; Below average: 70-89; Well below average: $\leq$ 69

## Summary Table for Classroom
```{r summary-table, echo = FALSE}

if(length(teacher_1) > 0){
  
  if(version == "EE"){
  student_data_for_table <- teacher_1 %>% 
    arrange(LastName) %>% 
    select("Student ID" = StudentID, Grade, "First Name" = FirstName, "Last Name" = LastName, "Overall" = OverallScore,
           "Emotion Recognition" = ERScore, "Social Perspective-Taking" = SPTScore, "Social Problem-Solving" = SPSScore, "Self Control" =
             SCScore) %>% 
    replace(is.na(.), "")
  } else if(version == "LE"){
    student_data_for_table <- teacher_1 %>% 
    arrange(LastName) %>% 
    select("Student ID" = StudentID, Grade, "First Name" = FirstName, "Last Name" = LastName, "Overall" = SEL.SS,
           "Understanding Others" = UO.SS, "Social Problem-Solving" = SPS.SS, "Self Control" = SC.SS) %>% 
    replace(is.na(.), "")
  }
  ### Summary Scores by School
  kable(student_data_for_table, "latex", booktabs = T, align = "lcllccccc", linesep = "") %>% 
    kable_styling(latex_options = c("striped", "bordered"), full_width = F) %>% 
    column_spec(2:9, width = "1.5cm") 
}  else {
  print("Not enough data collected in Timepoint 1")
  cat("\n\n\n")
}

cat('\n\n\n\n')

```

`r if(params$version =="EE") {"\\includepdf[pages={-}]{report_appendix.pdf}"}`
`r if(params$version =="LE") {"\\includepdf[pages={-}]{report_appendix_le.pdf}"}`
