---
mainfont: Nunito
font: Nunito
fontsize: 14 pt
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
    keep_tex: false
params: 
  file_path: data
  school_name: x
  set_title: x
geometry: "left=1in,right=1in,top=1in,bottom=0.6in"


---

\raggedright


```{r rmarkdown-setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")

#knitr::opts_chunk$set(fig.path = here::here("figs"))

options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)



```

```{r rmarkdown-prep, include=FALSE}
#add categorical variables (above, meets, etc.)
ee_data <- add_cat_vars(data)

#divide data into 2 timepoints
district <- subset(ee_data, ee_data$Timepoint==1) #remove NAs from school
district[] <- lapply(district, function(x) {if (is.numeric(x)) round(x, 0) else x}) #round to whole number


#create tables for each time point (each row = SCHOOL)
school_links_1 <- make_school_links(district, 1)

school_links_1_pdf <- school_links_1 %>%
  mutate(School = str_extract(School, "(?<=\\>).+?(?=\\<)")) %>% 
  replace(is.na(.), "")


#transform the data for summary plots
data_for_plotting_1 <- transform_for_plotting(district)

```

##  District-level report for `r  district_name`, Timepoint 1

This is a district-level report that shows student performance on SELweb EE in the `r district_name` district. 

The summary plot shows what proportion of students in the `r district_name` district fall into each of the 4 performance levels (above average, average, below average, and well-below average). The summary table shows the average standard score of students in in each school in
the `r district_name` district. See the attached appendix for more information about SELweb EE competencies, standard scores, and performance levels.

## Summary Plot for District
```{r setup-2, results = "asis"}

n_district <- length(district$ERScore[!is.na(district$ERScore)])

make_summary_plot_pdf(data_for_plotting_1, district_name, n_district)

cat('\n\n\n\n')
cat(' \n')

```
Above average: $\geq$ 115; At or around average: 90-114; Below average: 70-89; Well below average: $\leq$ 69


## Summary Table for District
```{r summary-table, results = "asis"}

## Summary Scores by School
kable(school_links_1_pdf, "latex", booktabs = T, align = "lccccccc", linesep = "") %>%
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>%
  column_spec(2:7, width = "1.5cm") %>% 
  column_spec(1, width = "4cm")

cat('\n\n\n\n')

```

\includepdf[pages={-}]{report_appendix.pdf}
