---
mainfont: Nunito
font: Nunito
fontsize: 14 pt
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
    keep_tex: false
params: 
  file_path: data
  school_name: x
  set_title: x
  version: x
geometry: "left=1in,right=1in,top=1in,bottom=0.6in"



---


```{r rmarkdown-setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)

```


```{r setup, include=FALSE}
#    vertical_layout: scroll

#prepare Timepoint2 datasets
district_time2 <- subset(new_data, new_data$School != "NA" & new_data$Timepoint==2) 
district_time2[] <- lapply(district_time2, function(x) {if (is.numeric(x)) round(x, 0) else x}) #round to whole number

if(version == "EE"){
  school_links_2 <- make_school_links(district_time2, 2)
  data_for_plotting_2 <- transform_for_plotting(district_time2)

} else if(version == "LE"){
  school_links_2 <- make_school_links_le(district_time2, 2)
  data_for_plotting_2 <- transform_for_plotting_le(district_time2)
}


school_links_2_pdf <- school_links_2 %>%
  mutate(School = str_extract(School, "(?<=\\>).+?(?=\\<)")) %>% 
  replace(is.na(.), "")


```


##  District-level report for `r  district_name`, Timepoint 2

This is a district-level report that shows student performance on SELweb `r  params$version` in the `r district_name` district. 

The summary plot shows what proportion of students in the `r district_name` district fall into each of the 4 performance levels (above average, average, below average, and well-below average). The summary table shows the average standard score of students in in each school in the `r district_name` district. See the attached appendix for more information about SELweb `r  params$version` competencies, standard scores, and performance levels.

## Summary Plot for District
```{r setup-pdf, echo = FALSE, warning = FALSE, results = "asis"}

#source("/Volumes/GoogleDrive/My\ Drive/xSEL\ Labs/Scripts/Dashboards/flexdashboard/reports/2019-2020/PDF_Mar2020/make_summary_plot_function_pdf.R")



if(version == "EE"){
  n_district_2 <- length(district_time2$ERScore[!is.na(district_time2$ERScore)])
  make_summary_plot_pdf(data_for_plotting_2, district_name, n_district_2)
} else if(version == "LE"){
  n_district_2 <- length(district_time2$UO.SS[!is.na(district_time2$UO.SS)])
  make_summary_plot_pdf_le(data_for_plotting_2, district_name, n_district_2)

}


#paste0(district_name, " (N = ", n_district_2, ")")

cat('\n\n\n\n')
cat("  \n")  
```
Above average: $\geq$ 115; At or around average: 90-114; Below average: 70-89; Well below average: $\leq$ 69

## Summary Table for District
```{r summary-table, warning = FALSE, echo = FALSE}


#names(school_links_1_pdf)[2:3] <- c("Number of\nchildren", "Overall\nScore")

### Summary Scores by School
kable(school_links_2_pdf, "latex", booktabs = T, align = "lccccccc", linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>% 
  column_spec(2:7, width = "2cm")


cat('\n\n\n\n')

```

`r if(params$version =="EE") {"\\includepdf[pages={-}]{report_appendix.pdf}"}`
`r if(params$version =="LE") {"\\includepdf[pages={-}]{report_appendix_le.pdf}"}`

