---
mainfont: Nunito
font: Nunito
fontsize: 14 pt
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
    keep_tex: false
params: 
  file_path: data
  school_name: x
  set_title: x
  version: x
geometry: "left=1in,right=1in,top=1in,bottom=0.6in"



---

```{r rmarkdown-setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)

```



```{r setup, include=FALSE}
#source("/Volumes/GoogleDrive/My\ Drive/xSEL\ Labs/Scripts/Dashboards/flexdashboard/functions/EE/plot_change_over_time_ee_function_pdf.R")
  
common_students <- intersect(district$StudentID, district_time2$StudentID)

#common <- district_time2[(district_time2$StudentID %in% district$StudentID),]

district_common_1 <- district[(district$StudentID %in% common_students),]
district_common_2 <- district_time2[(district_time2$StudentID %in% common_students),]



```

##  District-level report for `r  district_name`, Change Over Time

This is a district-level report that compares student performance on SELweb `r  params$version` in the `r district_name` district across both timepoints (usually Spring vs Fall). Only the students who completed SELweb both times are included in this report. 

The summary plot shows what proportion of students in the `r district_name` district fall into each of the 4 performance levels at each timepoint. The summary table compares standard scores for SELweb EE competencies for students in each school in the `r district_name` district across the two timepoints. See the attached appendix for more information about SELweb `r  params$version` competencies, standard scores, and performance levels.

## Summary Plot for District
```{r summary-plot, echo = FALSE, warning = FALSE}
if(version == "EE"){
  district_time1_plotting <- transform_for_plotting(district_common_1)
  district_time2_plotting <- transform_for_plotting(district_common_2)
} else if(version == "LE"){
  district_time1_plotting <- transform_for_plotting_le(district_common_1)
  district_time2_plotting <- transform_for_plotting_le(district_common_2)
}

data_for_plotting_change_1 <- district_time1_plotting %>% 
  mutate(Timepoint = "Fall")

data_for_plotting_change_2 <- district_time2_plotting %>% 
  mutate(Timepoint = "Spring")

data_for_plotting_change <- rbind(data_for_plotting_change_1, data_for_plotting_change_2)

if(version == "EE"){
  plot_change_over_time_ee_pdf(data_for_plotting_change, district_name, dim(district_common_2)[1])
} else if(version == "LE"){
  plot_change_over_time_le_pdf(data_for_plotting_change, district_name, dim(district_common_2)[1])
}

cat('\n\n\n\n')
cat("  \n")  
```
Above average: $\geq$ 115; At or around average: 90-114; Below average: 70-89; Well below average: $\leq$ 69

## Summary Table for District
```{r summary-table, warning = FALSE, echo = FALSE}

if(version == "EE"){
  merged_school_links_pdf <- left_join(school_links_1_pdf, school_links_2_pdf, by = "School") %>% 
  select(School, Fall = "Number of children.x", Spring = "Number of children.y", Fall = "Overall Score.x", Spring = "Overall Score.y",
         Fall = "Emotion Recognition.x", Spring = "Emotion Recognition.y", Fall = "Social Perspective-Taking.x", Spring = "Social Perspective-Taking.y", Fall = "Social Problem-Solving.x", Spring = "Social Problem-Solving.y", Fall = "Self Control.x",
         Spring = "Self Control.y") %>% 
  replace(is.na(.), "")
  
  kable(merged_school_links_pdf, "latex", booktabs = T, align = "lcccccccccccc", linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position", "bordered"), full_width = F) %>% 
  add_header_above(c("", "N" = 2, "Overall" = 2, "Emotion \nRecognition" = 2, "Social \nPerspective-\nTaking" = 2,
                     "Social \nProblem-\nSolving" = 2, "Self Control" = 2)) %>% 
  column_spec(2:13, width = "0.8cm") 

} else if(version == "LE"){
  merged_school_links_pdf <- left_join(school_links_1_pdf, school_links_2_pdf, by = "School") %>% 
  select(School, Fall = "Number of children.x", Spring = "Number of children.y", Fall = "Overall SEL.x", Spring = "Overall SEL.y",
         Fall = "Understanding Others.x", Spring = "Understanding Others.y",Fall = "Social Problem-Solving.x", Spring = "Social Problem-Solving.y", Fall = "Self Control.x",
         Spring = "Self Control.y") %>% 
  replace(is.na(.), "")
  
  kable(merged_school_links_pdf, "latex", booktabs = T, align = "lccccccccccc", linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position", "bordered"), full_width = F) %>% 
  add_header_above(c("", "N" = 2, "Overall" = 2, "Understanding \nOthers" = 2, "Social \nProblem-\nSolving" = 2, "Self Control" = 2)) %>% 
  column_spec(2:12, width = "0.8cm") 
}

### Summary Scores by School



cat('\n\n\n\n')

```

`r if(params$version =="EE") {"\\includepdf[pages={-}]{report_appendix.pdf}"}`
`r if(params$version =="LE") {"\\includepdf[pages={-}]{report_appendix_le.pdf}"}`

