---
params: 
  file_path: x
  school_name: x
  teacher_name: x
  set_title: x
  student_id: x
  version: x
header-includes:
- \input{header.tex}
mainfont: Nunito
font: Nunito
geometry: "left=1in,right=1in,top=1in,bottom=0.6in"
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: false


---


```{r rmarkdown-setup, include=FALSE}
#fontsize: 14pt
#\usepackage{array}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)

```

```{r pdf, echo = FALSE, warning = FALSE, results = "asis"}


#prepare data for tables

#step 1: figure confidence intervals
#step 2: reorganize data so that data are in long format by student with scores and CI_85

if(version == "EE"){
  if(params$student_id %in% district$StudentID & params$student_id %in% district_time2$StudentID){
    student1 <- prep_for_individ_plot(district, params$student_id)
    student2 <- prep_for_individ_plot(district_time2, params$student_id)
    student_comb <- rbind(student1, student2) %>% mutate(Score = value)
    dot_shape <- c(16, 18)
  } else if(params$student_id %in% district$StudentID){
    student_comb <- prep_for_individ_plot(district, params$student_id)
    dot_shape <- c(16)
  } else if(params$student_id %in% district_time2$StudentID){
    student_comb <- prep_for_individ_plot(district_time2, params$student_id)
    dot_shape <- c(17)
  }
} else if(version == "LE"){
  if(params$student_id %in% district$StudentID & params$student_id %in% district_time2$StudentID){
    student1 <- prep_for_individ_plot_le(district, params$student_id)
    student2 <- prep_for_individ_plot_le(district_time2, params$student_id)
    student_comb <- rbind(student1, student2) %>% mutate(Score = value)
    dot_shape <- c(16, 18)
  } else if(params$student_id %in% district$StudentID){
    student_comb <- prep_for_individ_plot_le(district, params$student_id)
    dot_shape <- c(16)
  } else if(params$student_id %in% district_time2$StudentID){
    student_comb <- prep_for_individ_plot_le(district_time2, params$student_id)
    dot_shape <- c(17)
  }
  
}

student_comb$Timepoint <- as.factor(student_comb$Timepoint)

```




##  Individual student report for `r  as.integer(params$student_id)`, Last Name: `r student_comb$LastName[1]`
### School: `r  params$school_name`
### Classroom: `r  params$teacher_name`

```{r plot, echo = FALSE, warning = FALSE, results = "asis"}

if(version == "EE"){
  plot <- ggplot(data = student_comb, aes(x=variable, y = Score, ymin = 50, ymax = 150, shape = Timepoint)) + #, group = Timepoint
    geom_point(aes(text = Score), color="black", fill = "black", size=3, position=position_dodge(0.5)) + 
    scale_shape_manual(values=dot_shape) + 
    geom_rect(aes(xmin = .5, xmax = 5.5, 
                  ymin = 50, ymax = 70, text = "Well-below"), fill = color_palette_dark_light[1], alpha = .1) +
    geom_rect(aes(xmin = .5,xmax = 5.5,
                  ymin = 70, ymax = 90, text = "Below"), fill = color_palette_dark_light[2], alpha = .1) +
    geom_rect(aes(xmin = .5, xmax = 5.5,
                  ymin = 90, ymax = 115, text = "Average"), fill = color_palette_dark_light[3], alpha = .1) + 
    geom_rect(aes(xmin = .5, xmax = 5.5,
                  ymin = 115, ymax = 150, text = "Above"), fill = color_palette_dark_light[4], alpha = .1) +
    geom_errorbar(aes(ymin=Score-CI_85, ymax=Score+CI_85), width=.1, colour="black", position=position_dodge(.5), alpha = .2) + 
    labs(y= "Score") + #, title=paste0(student_comb$District," - ", student_comb$School, " - ", student_comb$StudentID)
    theme(axis.title.x = element_blank(), 
          text = element_text(size=10, family = "Nunito"), panel.background = element_blank(),
          axis.text.x = element_text(hjust = .5),
          legend.title=element_text(size=9, family = "Nunito"),
          legend.text = element_text(size=9, family = "Nunito")) +
    geom_text(aes(label = round(Score+CI_85, 0), y = Score+CI_85), vjust = -.5, size = 2, position=position_dodge(.5)) +
    geom_text(aes(label = round(Score-CI_85, 0), y = Score-CI_85), vjust = 1.5, size = 2, position=position_dodge(.5)) + 
    ylim(50, 150)
} else if(version == "LE"){
   plot <- ggplot(data = student_comb, aes(x=variable, y = Score, ymin = 50, ymax = 150, shape = Timepoint)) + #, group = Timepoint
    geom_point(aes(text = Score), color="black", fill = "black", size=3, position=position_dodge(0.5)) + 
    scale_shape_manual(values=dot_shape) + 
    geom_rect(aes(xmin = .5, xmax = 4.5, 
                  ymin = 50, ymax = 70, text = "Well-below"), fill = color_palette_dark_light[1], alpha = .1) +
    geom_rect(aes(xmin = .5,xmax = 4.5,
                  ymin = 70, ymax = 90, text = "Below"), fill = color_palette_dark_light[2], alpha = .1) +
    geom_rect(aes(xmin = .5, xmax = 4.5,
                  ymin = 90, ymax = 115, text = "Average"), fill = color_palette_dark_light[3], alpha = .1) + 
    geom_rect(aes(xmin = .5, xmax = 4.5,
                  ymin = 115, ymax = 150, text = "Above"), fill = color_palette_dark_light[4], alpha = .1) +
    geom_errorbar(aes(ymin=Score-CI_85, ymax=Score+CI_85), width=.1, colour="black", position=position_dodge(.5), alpha = .2) + 
    labs(y= "Score") + #, title=paste0(student_comb$District," - ", student_comb$School, " - ", student_comb$StudentID)
    theme(axis.title.x = element_blank(), 
          text = element_text(size=10, family = "Nunito"), panel.background = element_blank(),
          axis.text.x = element_text(hjust = .5),
          legend.title=element_text(size=9, family = "Nunito"),
          legend.text = element_text(size=9, family = "Nunito")) +
    geom_text(aes(label = round(Score+CI_85, 0), y = Score+CI_85), vjust = -.5, size = 2, position=position_dodge(.5)) +
    geom_text(aes(label = round(Score-CI_85, 0), y = Score-CI_85), vjust = 1.5, size = 2, position=position_dodge(.5)) + 
    ylim(50, 150)
}

print(plot)





 # annotate("rect", xmin = .5, xmax = 5.5, ymin = 50, ymax = 70, fill = '#45874C', alpha = .6, label = "well-below") +
    # annotate("rect", xmin = .5,xmax = 5.5, ymin = 70, ymax = 90, fill = '#86C17D', alpha = .6) +
    # annotate("rect", xmin = .5, xmax = 5.5, ymin = 90, ymax = 115,fill = '#C0E4B8', alpha = .6) + 
    # annotate("rect", xmin = .5, xmax = 5.5, ymin = 115, ymax = 150, fill = '#EFF7EA', alpha = .6) +
  
  
  

```
<br>
<br>
<br>
  
This is a report of student’s performance on SELweb `r params$version` Scores from different timepoints are represented by different symbols. 
The report shows the student’s overall SELweb performance, as well as performance on each of the SELweb `r params$version` competencies.

Scores on all assessments contain some uncertainty. That means that the score a student achieves on an assessment is an estimate of his or her true ability. The error bars indicate the range of scores within which the student’s true score is 85% likely to fall.

Shades of green correspond to each of the 4 performance levels (ligher colors indicating higher performance).
The attached appendix provides more information about SELweb `r params$version` competencies, standard scores, and
performance levels.
<br>
<br>


`r if(params$version =="EE") {"\\includepdf[pages={-}]{report_appendix.pdf}"}`
`r if(params$version =="LE") {"\\includepdf[pages={-}]{report_appendix_le.pdf}"}`
