---
mainfont: Nunito
font: Nunito
fontsize: 14 pt
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
    keep_tex: false
params: 
  file_path: data
  school_name: x
  set_title: x
geometry: "left=1in,right=1in,top=1in,bottom=0.6in"


---

```{r rmarkdown-setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)

```


```{r setup, include=FALSE}

school_rel <- district %>% 
  filter(School == params$school_name) 

teacher_links_1 <- make_teacher_links(school_rel,1)

teacher_links_1_pdf <- teacher_links_1 %>%
  mutate(Teacher = str_extract(Teacher, "(?<=\\>).+?(?=\\<)")) %>%
  select(-1) %>% 
  replace(is.na(.), "")


school_for_plotting_1 <- prep_school_plots(district)

#school_level_time1 <- teacher_links_1_pdf[teacher_links_1_pdf$School==params$school_name,2:9]

grades_for_plotting_1 <- prep_grade_level_plots(district)

```

##  School-level report for `r  params$school_name`

This is a school-level report that shows student performance on SELweb EE aggregated across `r params$school_name`. 
The summary plot shows what proportion of students in`r params$school_name` fall into each of the 4 competency levels based on national norms (above average, average, below average, and well-below average). The summary table shows standard scores for SELweb EE competencies for each classroom within `r params$school_name`. 


## Summary Plot for School
```{r setup-pdf, echo = FALSE, warning = FALSE, results = "asis"}

#source("/Volumes/GoogleDrive/My\ Drive/xSEL\ Labs/Scripts/Dashboards/flexdashboard/reports/2019-2020/PDF_Jan2020/make_summary_plot_function_pdf.R")


n_school <- dim(subset(district, district$School == params$school_name))[1]

if(n_school >= 5){
  
data_1 <- school_for_plotting_1[school_for_plotting_1$School==params$school_name,]

#make_summary_plot(data_1, params$school_name, n_school)
make_summary_plot_pdf(data_1, params$school_name, n_school)

} else{
  
  print("Not enough data collected in Timepoint 1")
}

cat('\n\n\n\n')
cat("  \n")  

```
Above average: $\geq$ 115; At or around average: 90-114; Below average: 70-89; Well below average: $\leq$ 69


## Summary Table for School
```{r summary-table, echo = FALSE}


### Summary Scores by School
kable(teacher_links_1_pdf, "latex", booktabs = T, align = "lccccccc", linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>% 
  column_spec(2:7, width = "2cm")


cat('\n\n\n\n')

```



