---
mainfont: Nunito
font: Nunito
fontsize: 14 pt
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
    keep_tex: false
params: 
  file_path: data
  school_name: "Momentous School"
  set_title: x
  version: x
geometry: "left=1in,right=1in,top=1in,bottom=0.6in"


---

```{r rmarkdown-setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)

```


```{r setup, include=FALSE}

school_rel <- district %>% 
  filter(School == params$school_name) 

if(version == "EE"){
  teacher_links_1 <- make_teacher_links(school_rel,1)
} else if(version == "LE"){
  teacher_links_1 <- make_teacher_links_le(school_rel,1)
}

teacher_links_1_pdf <- teacher_links_1 %>%
  mutate(Teacher = str_extract(Teacher, "(?<=\\>).+?(?=\\<)")) %>%
  select(-1) %>% 
  replace(is.na(.), "")

if(version == "EE"){
  school_for_plotting_1 <- prep_school_plots(district)
  grades_for_plotting_1 <- prep_grade_level_plots(district)
} else if(version == "LE"){
  school_for_plotting_1 <- prep_school_plots_le(district)
  grades_for_plotting_1 <- prep_grade_level_plots_le(district)
}

```

##  School-level report for `r  params$school_name`, Timepoint 1

This is a school-level report that shows student performance on SELweb `r  params$version` in `r params$school_name`. 

The summary plot shows what proportion of students in `r params$school_name` all into each of the 4 performance levels (above average, average, below average, and well-below average). The summary table shows the average standard score of students in in each classroom in `r params$school_name`. See the attached appendix for more information about SELweb `r  params$version` competencies, standard scores, and performance levels. 


## Summary Plot for School
```{r setup-pdf, echo = FALSE, warning = FALSE, results = "asis"}

n_school <- dim(subset(district, district$School == params$school_name))[1]

if(n_school >= 5){
  data_1 <- school_for_plotting_1[school_for_plotting_1$School==params$school_name,]

  #make_summary_plot(data_1, params$school_name, n_school)
  if(version == "EE"){
    make_summary_plot_pdf(data_1, params$school_name, n_school)
  } else if(version == "LE"){
    make_summary_plot_pdf_le(data_1, params$school_name, n_school)
  }

} else{
  
  print("Not enough data collected in Timepoint 1")
}

cat('\n\n\n\n')
cat("  \n")  

```
Above average: $\geq$ 115; At or around average: 90-114; Below average: 70-89; Well below average: $\leq$ 69


## Summary Table for School
```{r summary-table, echo = FALSE}


### Summary Scores by School
kable(teacher_links_1_pdf, "latex", booktabs = T, align = "lccccccc", linesep = "") %>% 
  kable_styling(latex_options = c("striped", "hold_position"), full_width = F) %>% 
  column_spec(2:7, width = "2cm")


cat('\n\n\n\n')

```


`r if(params$version =="EE") {"\\includepdf[pages={-}]{report_appendix.pdf}"}`
`r if(params$version =="LE") {"\\includepdf[pages={-}]{report_appendix_le.pdf}"}`
