---
mainfont: Nunito
font: Nunito
fontsize: 14 pt
output:
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: header.tex
    keep_tex: false
params: 
  file_path: data
  school_name: x
  set_title: x
  version: x
geometry: "left=1in,right=1in,top=1in,bottom=0.6in"


---

```{r rmarkdown-setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(dev = "cairo_pdf")
options(knitr.kable.NA = "")
options(kableExtra.latex.load_packages = FALSE)

```



```{r setup, include=FALSE}
#source("/Volumes/GoogleDrive/My\ Drive/xSEL\ Labs/Scripts/Dashboards/flexdashboard/functions/EE/plot_change_over_time_ee_function_pdf.R")
  
common_students <- intersect(district$StudentID, district_time2$StudentID)

#common_students <- intersect(district[district$School==params$school_name,]$TeacherLast, district_time2[district_time2$School==params$school_name,]$TeacherLast)


school_common_1 <- district[(district$StudentID %in% common_students & 
                               district$School== params$school_name),]

school_common_2 <- district_time2[(district_time2$School == params$school_name & 
                                     district_time2$StudentID %in% common_students),]
```
##  School-level report for `r  params$school_name`, Change Over Time

This is a school-level report that compares student performance on SELweb `r params$version` in `r params$school_name` across both timepoints (usually Spring vs Fall). Only the students who completed SELweb both times are included in this report. 

The summary plot shows what proportion of students in the `r params$school_name` fall into each of the 4 performance levels at each timepoint. The summary table compares standard scores for SELweb EE competencies for students in each classroom in `r params$school_name`  across the two timepoints. See the attached appendix for more information about SELweb `r params$version` competencies, standard scores, and performance levels.

## Summary Plot for School
```{r summary-plot, echo = FALSE, warning = FALSE}

if(dim(school_common_1)[1] >=10 & dim(school_common_2)[1] >= 10){
  if(version == "EE"){
    school_time1_plotting <- transform_for_plotting(school_common_1)
    school_time2_plotting <- transform_for_plotting(school_common_2)
  } else if(version == "LE"){
    school_time1_plotting <- transform_for_plotting_le(school_common_1)
    school_time2_plotting <- transform_for_plotting_le(school_common_2)
  }

  data_1 <- school_time1_plotting %>% 
  mutate(Timepoint = "Fall")

  data_2 <- school_time2_plotting %>% 
    mutate(Timepoint = "Spring")

  data_change <- rbind(data_1, data_2) 
  if(version == "EE"){
    plot_change_over_time_ee_pdf(data_change, params$school_name, dim(school_common_1)[1])
  } else if(version== "LE"){
    plot_change_over_time_le_pdf(data_change, params$school_name, dim(school_common_1)[1])
  }



} else {
  print("Not enough data collected at both time points")
  
}

cat('\n\n\n\n')
cat("  \n")  

```
Above average: $\geq$ 115; At or around average: 90-114; Below average: 70-89; Well below average: $\leq$ 69

## Summary Table for School
```{r summary-table, warning = FALSE, echo = FALSE}

if(version == "EE"){
  merged_teacher_links_pdf <- left_join(teacher_links_1_pdf, teacher_links_2_pdf, by = c("Teacher", "Grade")) %>% 
  select(Teacher, Grade, Fall = "Number of children.x", Spring = "Number of children.y", Fall = "Overall Score.x", Spring = "Overall Score.y",
         Fall = "Emotion Recognition.x", Spring = "Emotion Recognition.y", Fall = "Social Perspective-Taking.x", Spring = "Social Perspective-Taking.y", Fall = "Social Problem-Solving.x", Spring = "Social Problem-Solving.y", Fall = "Self Control.x",
         Spring = "Self Control.y") %>% 
  replace(is.na(.), "")
  
  ### Summary Scores by School
  kable(merged_teacher_links_pdf, "latex", booktabs = T, align = "lccccccccccccc", linesep = "") %>% 
    kable_styling(latex_options = c("striped", "hold_position", "bordered"), full_width = F) %>% 
    add_header_above(c("", "", "N" = 2, "Overall" = 2, "Emotion \nRecognition" = 2, "Social \nPerspective-\nTaking" = 2,
                     "Social \nProblem-\nSolving" = 2, "Self Control" = 2)) %>% 
    column_spec(2:13, width = "0.8cm") 


} else if(version == "LE"){
  merged_teacher_links_pdf <- left_join(teacher_links_1_pdf, teacher_links_2_pdf, by = c("Teacher", "Grade")) %>% 
  select(Teacher, Grade, Fall = "Number of children.x", Spring = "Number of children.y", Fall = "Overall SEL.x", Spring = "Overall SEL.y",
         Fall = "Understanding Others.x", Spring = "Understanding Others.x", Fall = "Social Problem-Solving.x", Spring = "Social Problem-Solving.y", Fall = "Self Control.x",
         Spring = "Self Control.y") %>% 
  replace(is.na(.), "")
  
  kable(merged_teacher_links_pdf, "latex", booktabs = T, align = "lcccccccccccc", linesep = "") %>% 
    kable_styling(latex_options = c("striped", "hold_position", "bordered"), full_width = F) %>% 
    add_header_above(c("", "", "N" = 2, "Overall" = 2, "Understanding \nOthers" = 2,
                     "Social \nProblem-\nSolving" = 2, "Self Control" = 2)) %>% 
    column_spec(2:12, width = "0.8cm") 
}




cat('\n\n\n\n')

```

`r if(params$version =="EE") {"\\includepdf[pages={-}]{report_appendix.pdf}"}`
`r if(params$version =="LE") {"\\includepdf[pages={-}]{report_appendix_le.pdf}"}`
